Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2018-01-20 Thesis/Thesis.rnw
Improved figures, wording tweaks

In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}

@@

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRegionAAP.tex}
\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while when protection by palivizumab --- when administered per the AAP guidelines ---  is active}
\label{fig:coverageByRegionAAP}
\end{center}
\end{figure}

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans) + 
    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype=3, data=thresholds) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype=3, data=thresholds) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_x_continuous(breaks=epiWeekBreaks, labels=epiWeekLabels, limits=c(1, 52)) + 
        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
        scale_fill_manual(labels=spanLabels, values=twoToneAlt) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
        labs(x=NULL, y="Cumulative indicence fraction") + 
        theme(
            panel.grid.major.x=element_blank(),
            panel.grid.minor.x=element_blank(),
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
            legend.position="bottom"
        )

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        scale_x_discrete(labels=roundingLabels) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
            width=.25, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=rounding, color=strat), position=position_dodge(.5), size=.75) +
        labs(x="Calendrical rounding", y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        theme(
            legend.position="bottom"
        )
    dev.off()
@

@@

\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRoundingRegimen.tex}
\caption[The effect of calendrical rounding of start and end of RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of using an alternate regimen over the existing AAP-recommended regimen. Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
\label{fig:coverageByRoundingRegimen}
\end{center}
\end{figure*}

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoToneAlt, each=3), grey(0))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

@@

\setcounter{figure}{7}
\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone. Preventable fraction: fraction of RSV hospitalizations occurring while while the prophylaxis regimen offers protection}
\label{fig:coverageByRegionRegimenWithSliding}
\end{center}
\end{figure*}

@@

Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remainder of the prophylaxis regimen.

@@

Our attempt to optimize timing of the prophylaxis regimen (without changing its duration and therefore its cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, occurring primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).

>>>>

The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}

@@

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRegionAAP.tex}
\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
\label{fig:coverageByRegionAAP}
\end{center}
\end{figure}

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), data=spans, size=.375) + 
    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), data=spans, size=.375) + 
    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans, size=.375) + 
    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype="11", data=thresholds, size=.375) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype="11", data=thresholds, size=.375) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.end), data=thresholds, shape=18) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0), minor_breaks=epiWeekBreaks) +
        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
        scale_fill_manual(labels=spanLabels, values=twoToneAlt) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
        labs(x=NULL, y="Cumulative indicence fraction") + 
        theme(
            panel.grid.major.x=element_blank(),
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
            legend.position="bottom"
        )

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(15, 16, 17, 15, 16, 17, 15)) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(15, 16, 17, 15, 16, 17, 15)) + 
        scale_x_discrete(labels=roundingLabels) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
            width=.25, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=rounding, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(x="Calendrical rounding", y="Preventable fraction") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        theme(
            legend.position="bottom"
        )
    dev.off()
@

@@

\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRoundingRegimen.tex}
\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternate regimens over the AAP-recommended regimen. Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
\label{fig:coverageByRoundingRegimen}
\end{center}
\end{figure*}

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoToneAlt, each=3), grey(0))) + 
        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(15, 16, 17, 15, 16, 17, 15)) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

@@

\setcounter{figure}{7}
\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone. Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
\label{fig:coverageByRegionRegimenWithSliding}
\end{center}
\end{figure*}

@@

Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.

@@

Our attempt to optimize timing of the prophylaxis regimen (without changing its duration and therefore its cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
